Transitivity Simulation
========================================================

Question
--------------------------------------------------------

I would like to know how to interpret the size of your main result
is 4.11% a large or small amount of intransitivity? 
One easy way to do this is to simulate a logistic choice process, 
with different amounts of noise, and then compute your statistic to see where it falls.

Answer
--------------------------------------------------------

If preferences were completely random there would be 25% intransitivity.

Simulations
--------------------------------------------------------

### Simulation Functions

#### Row level intransitive calculation (simplified)

```{r}
comb.row.fn.sim <- function (df, comb.row) {
  # INPUT 
  #   df: individual participants data
  #   comb.row: comb data frame split by row
  j <- which((df$Image_left == comb.row$A | df$Image_right == comb.row$A) &
               (df$Image_left == comb.row$B | df$Image_right == comb.row$B))
  #Record choice for A vs B
  ApreftoB <- ifelse(df$Choice.image[j] == comb.row$A, 1, 0)
  
  #Find trial row in df that has the B vs C choice in comb
  k <- which((df$Image_left == comb.row$B | df$Image_right == comb.row$B) &
               (df$Image_left == comb.row$C | df$Image_right == comb.row$C))
  #Record choice for B vs C
  BpreftoC <- ifelse(df$Choice.image[k] == comb.row$B, 1, 0)
  
  #Find trial row in df that has the A vs C choice in comb
  l <- which((df$Image_left == comb.row$A | df$Image_right == comb.row$A) &
               (df$Image_left == comb.row$C | df$Image_right == comb.row$C))
  #Record choice for A vs C
  CpreftoA <- ifelse(df$Choice.image[l] == comb.row$C, 1, 0)
 
  #A triplet is intransitive if either A>B, B>C and C>A OR A<B, B<C and C<A (the second is the reverse)
  Intrans <- ifelse (ApreftoB == 1 & BpreftoC == 1 & CpreftoA == 1, 1, 
                     ifelse(ApreftoB == 0 & BpreftoC == 0 & CpreftoA == 0, 1, 0))
  
  # setup data to return
  ret.dat <- data.frame(A = comb.row$A, 
                        B = comb.row$B,
                        C = comb.row$C,
                        ApreftoB = ApreftoB,
                        BpreftoC = BpreftoC,
                        CpreftoA = CpreftoA,
                        Intrans = Intrans)
  return(ret.dat)
}
```

#### Apply row level intransitive calculation to each subject (simplified) 

```{r}
comb.fn.sim <- function(Data.cut) {
  images <- rep(1:20)
  comb.sim <- t(combn(images,3))
  comb.sim <- as.data.frame(comb.sim)
  names(comb.sim) <- c("A", "B", "C")
  comb.sim$ApreftoB <- rep(NA, nrow(comb.sim))
  comb.sim$BpreftoC <- rep(NA, nrow(comb.sim))
  comb.sim$CpreftoA <- rep(NA, nrow(comb.sim))
  comb.sim$Intrans <- rep(NA, nrow(comb.sim))
  comb.sim <- mutate(comb.sim, 
                 id = 1:nrow(comb.sim))
  ddply(comb.sim, .(id), comb.row.fn.sim, df = Data.cut)
}
```

### Got 25%

#### Rbinom choice P

```{r eval=FALSE}
create.new.data.rbinom <- function(){
  values <- rnorm(20, 0, 1)
  images <- rep(1:20)
  new.data <- as.data.frame(cbind(t(combn(values,2)), t(combn(images,2))))
  return(new.data)
}

simulate.choice.rbinom <- function(n){
  require(plyr)
  new.data <- ldply(as.data.frame(replicate(n, create.new.data.rbinom())),data.frame)
  names(new.data) <- c("f.id", "Value_left", "Value_right", "Image_left", "Image_right")
  
  new.data$Choice.left.P <- 1/(1+exp(new.data$Value_right - new.data$Value_left)) 
  
  new.data$Choice.left1.right0 <- round(new.data$Choice.left.P)
  
  new.data$Choice.left1.right0.binom <- rbinom(nrow(new.data), 1, 0.5)
  
  new.data$Choice.image <- ifelse(new.data$Choice.left1.right0.binom == 1, new.data$Image_left, new.data$Image_right)
  
  return(new.data)
}

sim.rbinom <- simulate.choice.rbinom(n = 50)
triplets.sim.rbinom <- ddply(sim.rbinom, .(f.id), comb.fn.sim)
intransitive.sim.rbinom <- ddply(triplets.sim.rbinom, .(f.id), summarise, 
                                  Intrans = sum(Intrans))
intransitive.sim.rbinom$PercentIntr <- intransitive.sim.rbinom$Intrans/1140*100
summary(intransitive.sim.rbinom$PercentIntr)

```

#### DEEP paper delta = N(0,1)

```{r eval=FALSE}

create.new.data.deep <- function(){
  values <- rnorm(20, 0, 1)
  images <- rep(1:20)
  delta <- rnorm(190, 0, 1)
  new.data <- as.data.frame(cbind(t(combn(values,2)), t(combn(images,2)), delta))
  return(new.data)
}

simulate.choice.deep <- function(n){
  require(plyr)
  new.data <- ldply(as.data.frame(replicate(n, create.new.data.deep())),data.frame)
  names(new.data) <- c("f.id", "Value_left", "Value_right", "Image_left", "Image_right", "delta")
  
  new.data$Choice.left.P <- 1/(1+exp(new.data$Value_right - new.data$Value_left)) 
  
  new.data$Choice.left1.right0 <- round(new.data$Choice.left.P)
  
  new.data$Choice.left.P.deep <- exp(new.data$delta * new.data$Value_left)/(exp(new.data$delta*new.data$Value_left) + exp(new.data$delta*new.data$Value_right))
  
  new.data$Choice.left1.right0.deep <- ifelse(new.data$Choice.left.P.deep >= 0.5, 1, 0)
  
  new.data$Choice.image <- ifelse(new.data$Choice.left1.right0.deep == 1, new.data$Image_left, new.data$Image_right)
  
  return(new.data)
}

sim.deep <- simulate.choice.deep(n = 50)
triplets.sim.deep <- ddply(sim.deep, .(f.id), comb.fn.sim)
intransitive.sim.deep <- ddply(triplets.sim.deep, .(f.id), summarise, 
                                  Intrans = sum(Intrans))
intransitive.sim.deep$PercentIntr <- intransitive.sim.deep$Intrans/1140*100
summary(intransitive.sim.deep$PercentIntr)

```

#### Add noise from rlogis(190, 0.5, 1) to choice P

```{r eval=FALSE}

create.new.data.rlogis <- function(){
  values <- rnorm(20, 0, 1)
  images <- rep(1:20)
  noise.rlogis <- rlogis(190, 0.5, 1)
  new.data <- as.data.frame(cbind(t(combn(values,2)), t(combn(images,2)), noise.rlogis))
  return(new.data)
}

simulate.choice.rlogis <- function(n, alpha){
  require(plyr)
  new.data <- ldply(as.data.frame(replicate(n, create.new.data.rlogis())),data.frame)
  names(new.data) <- c("f.id", "Value_left", "Value_right", "Image_left", "Image_right", "noise.rlogis")
  
  new.data$Choice.left.P <- 1/(1+exp(new.data$Value_right - new.data$Value_left)) 
  
  new.data$Choice.left1.right0 <- round(new.data$Choice.left.P)
  
  new.data$Choice.left.P.rlogis <- new.data$Choice.left.P + alpha*new.data$noise.rlogis
  
  new.data$Choice.left1.right0.rlogis <- ifelse(new.data$Choice.left.P.rlogis >= 0.5, 1, 0)
  
  new.data$Choice.image <- ifelse(new.data$Choice.left1.right0.rlogis == 1, new.data$Image_left, new.data$Image_right)
  
  return(new.data)
}

sim.rlogis <- simulate.choice.rlogis(n = 50, alpha = 1)
triplets.sim.rlogis <- ddply(sim.rlogis, .(f.id), comb.fn.sim)
intransitive.sim.rlogis <- ddply(triplets.sim.rlogis, .(f.id), summarise, 
                                  Intrans = sum(Intrans))
intransitive.sim.rlogis$PercentIntr <- intransitive.sim.rlogis$Intrans/1140*100
summary(intransitive.sim.rlogis$PercentIntr)


sim.rlogis.0.5 <- simulate.choice.rlogis(n = 50, alpha = 0.5)
triplets.sim.rlogis.0.5 <- ddply(sim.rlogis.0.5, .(f.id), comb.fn.sim)
intransitive.sim.rlogis.0.5 <- ddply(triplets.sim.rlogis.0.5, .(f.id), summarise, 
                                  Intrans = sum(Intrans))
intransitive.sim.rlogis.0.5$PercentIntr <- intransitive.sim.rlogis.0.5$Intrans/1140*100
summary(intransitive.sim.rlogis.0.5$PercentIntr)

sim.rlogis.2 <- simulate.choice.rlogis(n = 50, alpha = 2)
triplets.sim.rlogis.2 <- ddply(sim.rlogis.2, .(f.id), comb.fn.sim)
intransitive.sim.rlogis.2 <- ddply(triplets.sim.rlogis.2, .(f.id), summarise, 
                                  Intrans = sum(Intrans))
intransitive.sim.rlogis.2$PercentIntr <- intransitive.sim.rlogis.2$Intrans/1140*100
summary(intransitive.sim.rlogis.2$PercentIntr)
```

#### Add noise to values from N(0,1) at level alpha (THE RIGHT WAY CONTROLLING THE NOISE LEVEL)

```{r eval=FALSE}

create.new.data <- function(){
  values <- rnorm(20, 0, 1)
  images <- rep(1:20)
  noise.right <- rnorm(190, 0, 1)
  noise.left <-  rnorm(190, 0, 1)
  new.data <- as.data.frame(cbind(t(combn(values,2)), t(combn(images,2)), noise.right, noise.left))
  return(new.data)
}

simulate.choice <- function(n, alpha){
  require(plyr)
  new.data <- ldply(as.data.frame(replicate(n, create.new.data())),data.frame)
  names(new.data) <- c("f.id", "Value_left", "Value_right", "Image_left", "Image_right", "noise.left", "noise.right")
  
  new.data$Choice.left.P <- 1/(1+exp(new.data$Value_right - new.data$Value_left))
  
  new.data$Choice.left1.right0 <- round(new.data$Choice.left.P)
  
  new.data$Choice.left.P.noise <- 1/(1+exp(((1-alpha)*new.data$Value_right + (alpha * new.data$noise.right)) - 
                                       ((1-alpha)*new.data$Value_left + (alpha * new.data$noise.left))))
  
  new.data$Choice.left1.right0.noise <- ifelse(new.data$Choice.left.P.noise >= 0.5, 1, 0)
  
  
  new.data$Choice.image <- ifelse(new.data$Choice.left1.right0.noise == 1, new.data$Image_left, new.data$Image_right)
  return(new.data)
}
```

### Plot intransitivity at different noise levels w 1000 simulations

```{r warning=FALSE, message=FALSE}

setwd("~/Dropbox/CDS/Transitivity/grid files")
library(ggplot2)

load("sim.0.01.n.2014-05-06.RData")
load("sim.0.05.n.2014-05-06.RData")
load("sim.0.10.n.2014-05-06.RData")
load("sim.0.25.n.2014-05-06.RData")
load("sim.0.50.n.2014-05-06.RData")
load("sim.0.75.n.2014-05-06.RData")
load("sim.1.00.n.2014-05-06.RData")

sim.0.01.n.PIntr <- sim.0.01.n$intransitive.sims$PercentIntr
sim.0.05.n.PIntr <- sim.0.05.n$intransitive.sims$PercentIntr
sim.0.10.n.PIntr <- sim.0.10.n$intransitive.sims$PercentIntr
sim.0.25.n.PIntr <- sim.0.25.n$intransitive.sims$PercentIntr
sim.0.50.n.PIntr <- sim.0.50.n$intransitive.sims$PercentIntr
sim.0.75.n.PIntr <- sim.0.75.n$intransitive.sims$PercentIntr
sim.1.00.n.PIntr <- sim.1.00.n$intransitive.sims$PercentIntr

rm(sim.0.01.n, sim.0.05.n, sim.0.10.n, sim.0.25.n, sim.0.50.n, sim.0.75.n, sim.1.00.n, sim.0.01.PIntr, sim.0.05.PIntr, sim.0.10.PIntr, sim.0.25.PIntr, sim.0.50.PIntr, sim.0.75.PIntr, sim.1.00.PIntr)

PIntr <- data.frame(noise.level = c(rep(0.01, 1000), rep(0.05, 1000), rep(0.10, 1000), rep(0.25, 1000),rep(0.50, 1000), rep(0.75, 1000), rep(1.00, 1000)),
                    PercentIntr = c(sim.0.01.n.PIntr, sim.0.05.n.PIntr, sim.0.10.n.PIntr, sim.0.25.n.PIntr,sim.0.50.n.PIntr,sim.0.75.n.PIntr,sim.1.00.n.PIntr))

ggplot(data = PIntr, aes(x = as.factor(noise.level), y = PercentIntr))+
  geom_boxplot()+
  theme_classic()+
  xlab("Noise level")+
  ylab("Percent of Intransitivities")

median.intr.sim <- cbind(aggregate(PercentIntr ~ noise.level ,data = PIntr, FUN = median), aggregate(PercentIntr ~ noise.level ,data = PIntr, FUN = function(x){sd(x)/sqrt(1000)})[2])
names(median.intr.sim) <- c("Group", "MedianCleanIntr", "se")
median.intr.sim$ci.low <- median.intr.sim$MedianCleanIntr - median.intr.sim$se
median.intr.sim$ci.high <- median.intr.sim$MedianCleanIntr + median.intr.sim$se

ggplot(data = median.intr.sim, aes(x = Group, y = MedianCleanIntr))+
  geom_point()+
  geom_line()+
  geom_errorbar(ymin = median.intr.sim$ci.low, ymax =  median.intr.sim$ci.high, width = 0.03)+
  theme_classic()+
  xlab("Noise level")+
  ylab("Median Percent of Intransitivities")


### Changing number of options

load("sim.1.00.30.2014-05-12.RData")
load("sim.0.75.30.2014-05-12.RData")
load("sim.0.50.30.2014-05-12.RData")
load("sim.0.25.30.2014-05-12.RData")
load("sim.0.10.30.2014-05-12.RData")

sim.0.10.PIntr <- sim.0.10.30$intransitive.sims$PercentIntr
sim.0.25.PIntr <- sim.0.25.30$intransitive.sims$PercentIntr
sim.0.50.PIntr <- sim.0.50.30$intransitive.sims$PercentIntr
sim.0.75.PIntr <- sim.0.75.30$intransitive.sims$PercentIntr
sim.1.00.PIntr <- sim.1.00.30$intransitive.sims$PercentIntr


PIntr <- data.frame(noise.level = c(rep(0.10, 100), rep(0.25, 100),rep(0.50, 100), rep(0.75, 100), rep(1.00, 100)),
                    PercentIntr = c(sim.0.10.PIntr, sim.0.25.PIntr,sim.0.50.PIntr,sim.0.75.PIntr,sim.1.00.PIntr))

PIntr.n <- data.frame(noise.level = c(rep(0.10, 1000), rep(0.25, 1000),rep(0.50, 1000), rep(0.75, 1000), rep(1.00, 1000)),
                    PercentIntr = c(sim.0.10.n.PIntr, sim.0.25.n.PIntr,sim.0.50.n.PIntr,sim.0.75.n.PIntr,sim.1.00.n.PIntr))

ggplot(data = PIntr, aes(x = as.factor(noise.level), y = PercentIntr))+
  geom_boxplot()+
  theme_classic()+
  xlab("Noise level")+
  ylab("Percent of Intransitivities")

ggplot(data = PIntr.n, aes(x = as.factor(noise.level), y = PercentIntr))+
  geom_boxplot()+
  theme_classic()+
  xlab("Noise level")+
  ylab("Percent of Intransitivities")

load("sim.1.00.40.2014-05-12.RData")
load("sim.0.75.40.2014-05-12.RData")
load("sim.0.50.40.2014-05-12.RData")
load("sim.0.25.40.2014-05-12.RData")
load("sim.0.10.40.2014-05-12.RData")

sim.0.10.40.PIntr <- sim.0.10.40$intransitive.sims$PercentIntr
sim.0.25.40.PIntr <- sim.0.25.40$intransitive.sims$PercentIntr
sim.0.50.40.PIntr <- sim.0.50.40$intransitive.sims$PercentIntr
sim.0.75.40.PIntr <- sim.0.75.40$intransitive.sims$PercentIntr
sim.1.00.40.PIntr <- sim.1.00.40$intransitive.sims$PercentIntr


PIntr <- data.frame(noise.level = c(rep(0.10, 100), rep(0.25, 100),rep(0.50, 100), rep(0.75, 100), rep(1.00, 100)),
                    PercentIntr = c(sim.0.10.40.PIntr, sim.0.25.40.PIntr,sim.0.50.40.PIntr,sim.0.75.40.PIntr,sim.1.00.40.PIntr))

```