Intransitivity by lesion size plot reproduced for ISDN presentation.

```{r}
library(ggplot2)

talk.plot.df <- data.frame (Hippocampal_Ratio = c(0.03,0.031, 0.07, 0.09, 0.095, 0.10, 0.107, 0.115, 0.16, 0.18, 0.195, 0.2, 0.24, 0.255, 0.28, 0.36),
Intransitivity_Percent = c(3.2, 3.2, 4, 9, 7.6, 7.6, 6.5, 7.4, 6.3, 7.5, 7.5, 8, 9.5, 7.5, 22.5, 24.5))

library(Hmisc)

spearman.test(talk.plot.df$Hippocampal_Ratio, talk.plot.df$Intransitivity_Percent)

ggplot(talk.plot.df, aes(Hippocampal_Ratio, Intransitivity_Percent))+
  geom_point()+
  geom_smooth(method = "lm", color = "black")+
  theme_bw()+
  ylab("Mean Percentage of Intransitivities")+
  xlab("Hippocampal Ratio")+
  theme_bw()+
  theme(axis.title.y = element_text(face="bold", size = 20),
           axis.title.x  = element_text(face="bold", size = 20))
```

Following up on Ian Krajbich's suggestiion on fitting diffusion models to understand relationship between decision difficulty/indifference and reaction times

First look at difference between numbers in the control task and reaction time

```{r}
View(numbers.trial.data)

# Womp. I actually don't know what numbers the image numbers correspond to. Turns out the image numbers are the actual stimuli so can use those for decision difficulty.
numbers.trial.data$num.diff <- abs(numbers.trial.data$Image_left - numbers.trial.data$Image_right)


#The variance ofdifferences was the same for all groups (set up by experiment so manipulation check)
aggregate(num.diff ~ Group, FUN = var, numbers.trial.data)
ggplot(numbers.trial.data, aes(Group, num.diff))+
  geom_boxplot(width = 0.5)+
  theme_bw()+
  ylab("Difference in numbers")

#The easier the decision (the bigger the difference in values) the faster all groups got
#The control group appears faster compared to both lesion groups in the control task BUT this doesn't appear statistically significant in the regression
p1 <- ggplot(numbers.trial.data, aes(num.diff, RT, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Difference between numbers (Difficulty)")+
  ylab("Response times")
#No significan interactions or group differences. All groups are faster the larger the difference between the numbers (i.e. the easier the decisions)
summary(lmer(scale(RT) ~ scale(num.diff) * Group + (1|f.id), data = numbers.trial.data))

#Difference in values and intransitivity
#The lines are pretty flat. All the decisions seem pretty easy/equally likely to be involved in an intransitivity
ggplot(numbers.trial.data, aes(num.diff, IntransTripleCounted, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Difference between numbers (Difficulty)")+
  ylab("Number of Intransitivities Trial is involved in")

#Probability of being involved in intransitivity measure (new)
#How many times a trial involved in an intransitivity/total number intransitivities for subject

#Nominator: (IntransTripleCounted does indeed say how many times a trial was involved in an intransitive triplet)

#Denomiator:
numbers.trial.data <- merge(numbers.trial.data, both.Intransitive[as.character(both.Intransitive$Task) == "numbers", c("f.id", "CleanIntr")], by = "f.id", all.x = T)

#Prob of Intransitivity for a given trial
numbers.trial.data$ProbIntr <- (numbers.trial.data$IntransTripleCounted - numbers.trial.data$MisPressIntransTripleCounted) / (numbers.trial.data$CleanIntr*3)

#Check if probabilities for all subjects add up to 1. (yes.)
ddply(numbers.trial.data, c("f.id"), summarise, tot = sum(ProbIntr))

#There are a bunch of people with no intransitivities (so dividing by 0). Replace these with 0
numbers.trial.data$ProbIntr <- ifelse(is.na(numbers.trial.data$ProbIntr), 0, numbers.trial.data$ProbIntr)

#Back to decision difficulty and probability of intransitivity
#For all groups groups harder trials are more likely to be involved in intransitivities 
p2 <- ggplot(numbers.trial.data, aes(num.diff, ProbIntr, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Difference between numbers (Difficulty)")+
  ylab("Probability of Intransitivity")

summary(lmer(scale(ProbIntr) ~ scale(num.diff) * Group + (1|f.id), data = numbers.trial.data))

#Probability of transitivity stays the same across the task for the numbers task
p3 <- ggplot(numbers.trial.data, aes(Trialnumber, ProbIntr, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Trial Number")+
  ylab("Probability of Intransitivity")


library(gridExtra)
g <- ggplotGrob(p1 + theme(legend.position="bottom"))$grobs
legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]

p4 <- grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         p3 + theme(legend.position="none"),
                         nrow=1),
             legend, nrow=2,heights=c(10, 1),
             main = "Relationship between decision difficulty, RT and intransitivity in numbers task")
rm(g, legend)
```

So move to the second idea and look at choice data and decision difficulty. 

How can I get ordinal utilities per subject

```{r}
#How about just taking the difference of how many times they chose the item and avoid an artificial point system. This way ties will be indifference (0).If they haven't chosen an item assign a 0.

get.ordinal.value <- function(x){
  
  tmp <- data.frame(item = dimnames(sort(table(x$Choice.image)))[[1]],
                    value = sort(table(x$Choice.image)))
  
  return(tmp)
  }

# Does it work?
get.ordinal.value(choice2.trial.data[choice2.trial.data$SubjectID == 306,])
# Yes.

# So apply it to everyone's data
ordinal.value.df <- plyr::ddply(choice2.trial.data, c("f.id"), get.ordinal.value)

# A bit hacky but merge twice to assign right ordinal values to each image and then get value difference per trial.

#Merge 1 for image left
#KEEP ALL!
#RENAME col
choice2.trial.data.w.val <- merge(choice2.trial.data, ordinal.value.df, by.x = c("f.id","Image_left"), by.y = c("f.id","item"), all.x = T)
names(choice2.trial.data.w.val)[24] <- "value.left"

#Merge 2 for image right
choice2.trial.data.w.val <- merge(choice2.trial.data.w.val, ordinal.value.df, by.x = c("f.id","Image_right"), by.y = c("f.id","item"), all.x = T)
names(choice2.trial.data.w.val)[25] <- "value.right"

#Replace NAs in values with 0's
choice2.trial.data.w.val$value.left <- ifelse(is.na(choice2.trial.data.w.val$value.left), 0, choice2.trial.data.w.val$value.left)

choice2.trial.data.w.val$value.right <- ifelse(is.na(choice2.trial.data.w.val$value.right), 0, choice2.trial.data.w.val$value.right)

#Val.diff
#The smaller the difference the harder the decision
choice2.trial.data.w.val$val.diff <- abs(choice2.trial.data.w.val$value.left - choice2.trial.data.w.val$value.right)

#The variance of value differences was the same for all groups
#It's not like one group cared less about candy bars that they were just choosing randomly
aggregate(val.diff ~ Group, FUN = var, choice2.trial.data.w.val)
ggplot(choice2.trial.data.w.val, aes(Group, val.diff))+
  geom_boxplot(width = 0.5)+
  theme_bw()+
  ylab("Value difference")

#The easier the decision (the bigger the difference in values) the faster all groups got
#MTL group was consistently slower at all levels of value difference
p1 <- ggplot(choice2.trial.data.w.val, aes(val.diff, RT, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Value difference")+
  ylab("Response times")
#Significant interactions show that the how RTs change with decision difficulty differs by group. Though they all get faster at easier decisions the MTL group is consistently slower
summary(lmer(scale(RT) ~ scale(val.diff) * Group + (1|f.id), data = choice2.trial.data.w.val))
summary(lmer(scale(RT) ~ poly(val.diff, 2) * Group + (1|f.id), data = choice2.trial.data.w.val))

#Difference in values and intransitivity
#The harder the decision the more intransitivite triplets it is involved in
#This graph is deceptive because it suggests that for the MTL group trials that are closer to indifference are involved in more intransitivities but it's not normalized! (i.e. the trials are involved in more intransitivities but the MTL group makes more intransitivities to begin with, which is why the probability of intransitivity measure below in more descriptive) 
ggplot(choice2.trial.data.w.val, aes(val.diff, IntransTripleCounted, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Value difference")+
  ylab("Number of Intransitivities Trial is involved in")

#Probability of being involved in intransitivity measure (new)
#How many times a trial involved in an intransitivity/total number intransitivities for subject

#Nominator: (IntransTripleCounted does indeed say how many times a trial was involved in an intransitive triplet)

#Denomiator:
choice2.trial.data.w.val <- merge(choice2.trial.data.w.val, both.Intransitive[as.character(both.Intransitive$Task) == "choice", c("f.id", "CleanIntr")], by = "f.id", all.x = T)

#Prob of Intransitivity for a given trial
choice2.trial.data.w.val$ProbIntr <- (choice2.trial.data.w.val$IntransTripleCounted - choice2.trial.data.w.val$MisPressIntransTripleCounted) / (choice2.trial.data.w.val$CleanIntr*3)

#Check if probabilities for all subjects add up to 1. (yes.)
ddply(choice2.trial.data.w.val, c("f.id"), summarise, tot = sum(ProbIntr))

#Back to decision difficulty and probability of intransitivity
#For the MTL group harder trials (those where the value difference is smaller) are less likely to be involved in intransitivities suggesting that these decisions are not as hard for them because they have problems with retaining value
p2 <- ggplot(choice2.trial.data.w.val, aes(val.diff, ProbIntr, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Value difference")+
  ylab("Probability of Intransitivity")

summary(lmer(scale(ProbIntr) ~ scale(val.diff) * Group + (1|f.id), data = choice2.trial.data.w.val))

#Try making an graph to convey this point more easily
summary(choice2.trial.data.w.val$val.diff)

choice2.trial.data.w.val$difficulty.lab <- with(choice2.trial.data.w.val, ifelse(val.diff < 4, "Hard", ifelse(val.diff > 3 & val.diff < 10, "Medium", ifelse(val.diff>= 10, "Easy", NA))))

table(choice2.trial.data.w.val$difficulty.lab, useNA="ifany")

choice2.trial.data.w.val$difficulty.lab <- factor(choice2.trial.data.w.val$difficulty.lab, levels = c("Easy","Medium", "Hard"))

plot.valdiff.df <- cbind(aggregate(ProbIntr ~ difficulty.lab + Group, choice2.trial.data.w.val, mean),
aggregate(ProbIntr ~ difficulty.lab + Group, choice2.trial.data.w.val, se)[3])
names(plot.valdiff.df) <- c("Difficulty", "Group", "MeanP", "SEM")

ggplot(plot.valdiff.df, aes(Difficulty, MeanP, group = Group, fill = Group))+
  geom_bar(stat="identity", position = "dodge")+
  geom_errorbar(aes(ymin = MeanP-SEM, ymax = MeanP+SEM), position = position_dodge(0.9), width = 0.5)+
  theme_bw()+
  xlab("Value difference")+
  ylab("Probability of Intransitivity")+
scale_fill_grey(start = 0, end = .9)

ggsave("./TransitivityFigures/CleanFigure4.png", width=6, height=4, dpi=300)

plot.valdiff.rt.df <- cbind(aggregate(RT ~ difficulty.lab + Group, choice2.trial.data.w.val, mean),
aggregate(RT ~ difficulty.lab + Group, choice2.trial.data.w.val, se)[3])
names(plot.valdiff.rt.df) <- c("Difficulty", "Group", "MeanRT", "SEM")

ggplot(plot.valdiff.rt.df, aes(Difficulty, MeanRT, group = Group, fill = Group))+
  geom_bar(stat="identity", position = "dodge")+
  geom_errorbar(aes(ymin = MeanRT-SEM, ymax = MeanRT+SEM), position = position_dodge(0.9), width = 0.5)+
  theme_bw()+
  xlab("Value difference")+
  ylab("Response Time")+
scale_fill_grey(start = 0, end = .9)

p3 <- ggplot(choice2.trial.data.w.val, aes(Trialnumber, ProbIntr, group = Group, col = Group))+
  geom_smooth(method = "loess")+
  theme_bw()+
  xlab("Trial Number")+
  ylab("Probability of Intransitivity")

library(gridExtra)
g <- ggplotGrob(p1 + theme(legend.position="bottom"))$grobs
legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]

p4 <- grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         p3 + theme(legend.position="none"),
                         nrow=1),
             legend, nrow=2,heights=c(10, 1),
             main = "Relationship between decision difficulty, RT and intransitivity in preference task")
rm(g, legend)
```

```{r}
#IntransTripleCounted counts how many intransitive triplets a trial was involved in
#Each trial is part of ?? triplets
#Get back to this in a moment

#Exploring the distribution of value distributions for each group for now
#The idea is: if the value representation is unstable they will not be choosing the bounty over other bars every time even if that is their true preference
#So if we estimate value by counting how many times it was chosen over other bars then we will underestimate the value of most preferred bars and overestimate that of least preferred ones
#So the value differences for the MTL group should be smaller overall

#Two ways of visualizing this:
#Either by looking at the whole distribution of the value differences for each group (the earlier peak for the MTL group shows that all decisions were harder)
ggplot(choice2.trial.data.w.val, aes(val.diff, group = Group, fill = Group))+
  geom_density(alpha = 0.5)+
  theme_bw()

#Or my comparing the means (which is an accurate representation of the anova that follows): The C and ETL groups do not differ from each other while the MTL group is significantly lower than both
plot.valdiff.dist.df <- cbind(aggregate(val.diff ~ Group, choice2.trial.data.w.val, mean),
aggregate(val.diff ~ Group, choice2.trial.data.w.val, se)[2])
names(plot.valdiff.dist.df) <- c("Group", "mean.val.diff","sem.val.diff")

ggplot(plot.valdiff.dist.df, aes(Group, mean.val.diff))+
  geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "gray")+
  geom_errorbar(aes(ymin = mean.val.diff - sem.val.diff, ymax = mean.val.diff + sem.val.diff), position = position_dodge(0.9), width = 0.25)+
  theme_bw()

#Anova and pairwise t-test showing this group difference in distribution of value differences
summary(aov(val.diff ~ Group, data = choice2.trial.data.w.val))
with(choice2.trial.data.w.val, pairwise.t.test(val.diff, Group, p.adjust.method = "bonf"))

#So all the decisions are "harder" for the MTL group because the value representation is not stable as demonstrated by the smaller variance of the number of times each bar is chosen 

#SIDE NOTE:What would the variance be if they chose perfectly?

#Moreover the decrease in RT by value difference is not the same for each group
ggplot(choice2.trial.data.w.val, aes(val.diff, RT, group = Group, col = Group))+
  geom_smooth(method="lm")+
  theme_bw()

#Should I standardize the value difference distribution for this (since they differ by group)? 
#Scaling val.diff for each individual
choice2.trial.data.w.val <- ddply(choice2.trial.data.w.val, "f.id", mutate, c.val.diff = scale(val.diff))

#Now the means and variances for all groups are the same
summary(aov(c.val.diff ~ Group, data = choice2.trial.data.w.val))

#As seen by the distribution of the value differences as well
ggplot(choice2.trial.data.w.val, aes(c.val.diff, group = Group, fill = Group))+
  geom_density(alpha = 0.5)+
  theme_bw()

#Looking at how response times change with standardized value differences
ggplot(choice2.trial.data.w.val, aes(c.val.diff, RT, group = Group, col = Group))+
  geom_smooth(method = "lm")+
  theme_bw()

summary(lm(scale(RT) ~ c.val.diff * Group, data = choice2.trial.data.w.val))

#Is there a difference between the groups above and beyond the effect of "value difference"
choice2.trial.data.w.val$RT.val.diff.resid <- resid(lm(scale(RT) ~ c.val.diff, data=choice2.trial.data.w.val))

#If you take the effect of value diff out MTL is sig higher...(to be cont)
summary(lm(RT.val.diff.resid ~ Group, data = choice2.trial.data.w.val))

#NOT USEFUL? Does the variance of val.diff correlate significantly with the number of intransitivities (i.e. the more intransitivities the smaller the variance)
#Scatter plot
plot.valdiff.var <- ddply(choice2.trial.data.w.val, c("f.id", "Group", "CleanIntr"), summarise, 
      val.diff.spread = var(val.diff))

ggplot(plot.valdiff.var[plot.valdiff.var$CleanIntr<110,], aes(CleanIntr, val.diff.spread, col = Group, group = Group))+
  #geom_point()+
  geom_smooth(method="lm")+
  theme_classic()

summary(aov(val.diff.spread ~ Group*CleanIntr, data = plot.valdiff.var))
summary(lm(val.diff.spread ~ Group*CleanIntr, data = plot.valdiff.var))

```